Automated Verification of Stand-alone Solar Photovoltaic Systems

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
added comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong. It is important to evaluate how critical the load application is and the horizon of evaluation. However this analysis can be useful, for example, to improve the sized battery autonomy.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.

>>>>

With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong. It is important to evaluate how critical the load application is and the horizon of evaluation. However this analysis can be useful, for example, to improve the sized battery autonomy.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw \textcolor{red}{add a citation here}. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.
